ChIP-seq example

### 2019-12-18 analysis/chipseq.Rmd
wflow_publish("chipseq.Rmd")
Adjusted setup steps in a few of the R Markdown files.
Working on code to run HF method in chipseq example.

```{r load-pkgs, warning=FALSE, message=FALSE}
source("../code/chipseq.functions.R")
library(smashr)
library(ggplot2)
library(cowplot)
```

@@

Run SMASH
---------

@@

To provide a "baseline" to compare against the SMASH estimates, we
retrieve the peaks identified in the same ChIP-seq data using the MACS
software.

@@

Based on this plot, it is clear that the the strongest SMASH intensity
estimates align very closely with the peaks found by MACS.

Intriguingly, the SMASH estimates also suggest the presence of several
additional weaker peaks that were not identified by MACS.

>>>>

```{r load-pkgs, warning=FALSE, message=FALSE}
source("../code/chipseq.functions.R")
library(smashr)
library(ggplot2)
library(cowplot)
library(haarfisz)
```

@@

Run SMASH and Haar-Fisz methods
-------------------------------

The Haar-Fisz method transforms the Poisson counts, then applies
Gaussian wavelet methods to the transformed data.

```{r run-haar-fisz}
res.hf <- denoise.poisson(counts,meth.1 = hf.la10.ti4,cs.1 = 50,hybrid = FALSE)
```

@@

To provide a "baseline" to compare against the SMASH estimates, we
retrieve the peaks identified in the same ChIP-seq data using the MACS
software. Again, these data should have been included with the git
repository you downloaded.

@@

Based on this plot, it is clear that the the strongest SMASH intensity
estimates align very closely with the peaks found by MACS. Intriguingly,
the SMASH estimates also suggest the presence of several additional
weaker peaks that were not identified by MACS.

We compare the results against those produced by Haar-Fisz
```{r plot-smash-estimates-2, fig.height=3, fig.width=9}
create.chipseq.plot(bppos/1e6,counts,res.hf,(peaks$start + peaks$end)/2e6,
                    nbreaks = 80) +
  scale_x_continuous(limits = c(0.88,1.02),breaks = seq(0.88,1.02,0.02)) +
  scale_y_continuous(limits = c(-1,9),breaks = seq(0,8,2))
```
